Cooperative Decision Making for Communities of Autonomous Web Services

### 2013-12-14 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

    $\forall C_1,C_2 \subseteq N$
    \begin{itemize}
        \item {\color{red} convex:} $v(C_1) + v(C_2) \leq v(C_1 \bigcup C_2) + v(C_1 \bigcap C_2)$ Convexity has important properties in cooperative game theory solution concepts.
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution properties}
    Let $x \in R^n$ be a solution of the TU game $(N,v)$
    \begin{itemize}
        \item {\color{red} Feasible solution:} $\sum_{i \in N} x(i) \leq v(N)$
        \item {\color{red} Efficiency:} $x(N) = v(N)$
        \begin{itemize}
            \item the payoff distribution is an allocation of the entire worth of the grand coalition to all agents
        \end{itemize}
        \item {\color{red} Individual rationality:} $\forall i \in N, x(i) \geq v(\{i\})$
        \begin{itemize}
            \item player obtains at least its self-value of payoff
        \end{itemize}
        \item {\color{red} Group rationality:} $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
    \end{itemize}

@@

    \begin{definition} [Shapley Value]\label{dfn:shapleyvalue}
        Given a coalitional game $(N,v)$, the Shapley value of player $i$ is given by: \\
        $\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))$
    \end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some properties}
    \begin{itemize}
        \item The core may not always be non-empty
        \item Shapley value always exists and is unique.
        \item When the valuation function is {\color{red}superadditive}, the Shapley value is {\color{red}individually rational}, i.e., it is an imputation.
        \item When the valuation function is {\color{red}convex}, the Shapley value is also group rational, hence, it is in the {\color{red}core}.
        \item A convex game has a non-empty core
        \item There are other well-known solution concepts: The bargaining set, The nucleolus and The nucleolus.
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{$\epsilon$-Core}
    \begin{itemize}
        \item The core may not always be non-empty
        \item (To add some items)
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    \begin{itemize}
        \item Upon receiving membership request the master web service checks if the coalition will be stable having the new member.
        \item If the game is convex, core exists.
        \item If the game is convex, Shapley value is in core.
        \item Convexity Condition:
        \begin{center}
          $\forall S,T | S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N,$ \\
          $v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)$ \\
          $\Leftrightarrow$  \\
          $v(S' \cup T') \geq v(S') + v(T') - v(S' \cap T')$
        \end{center}
    \end{itemize}

@@

\begin{frame}{Scenario Two: Web Services and Many Communities}
    \begin{itemize}
        \item Based on Coalition Structure theory
        \begin{itemize}
            \item What coalitions to form?
            \item Stability in coalition structure, is a partition of players, where no other partition can provide all agents with better utility.
        \end{itemize}
        \item Has to be distributed not centralized
        \item Merge and Split Algorithm
        \begin{itemize}
            \item Iterative
            \item Converges to a final partition
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.5 \columnwidth]{figures/scenario2.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}       	
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Induced subgraph games}

>>>>

    $\forall C_1,C_2 \subseteq N$
    \begin{itemize}
        \item {\color{red} convex:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2) - v(C_1 \bigcap C_2)$. Convexity has important properties in cooperative game theory solution concepts.
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution properties}
    Let $x \in R^n$ be a solution of the TU game $(N,v)$
    \begin{itemize}
        \item {\color{red} Feasible solution:} $\sum_{i \in N} x(i) \leq v(N)$
        \item {\color{red} Efficiency:} $x(N) = v(N)$
        \begin{itemize}
            \item the payoff distribution is an allocation of the entire worth of the grand coalition to all agents
        \end{itemize}
        \item {\color{red} Individual rationality:} $\forall i \in N, x(i) \geq v(\{i\})$
        \begin{itemize}
            \item player obtains at least its self-value of payoff
        \end{itemize}
        \item {\color{red} Group rationality:} $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
    \end{itemize}

@@

    \begin{definition} [Shapley Value]\label{dfn:shapleyvalue}
        Given a coalitional game $(N,v)$, the Shapley value of player $i$ is given by: \\
        $\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))$
    \end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some properties}
    \begin{itemize}
        \item The core may not always be non-empty
        \item Shapley value always exists and is unique.
        \item When the valuation function is {\color{red}superadditive}, the Shapley value is {\color{red}individually rational}, i.e., it is an imputation.
        \item When the valuation function is {\color{red}convex}, the Shapley value is also group rational, hence, it is in the {\color{red}core}.
        \item A convex game has a non-empty core
        \item There are other well-known solution concepts: The bargaining set, The nucleolus and The nucleolus.
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    \begin{itemize}
        \item Upon receiving membership request the master web service checks if the coalition will be stable having the new member.
        \item If the game is convex, core exists.
        \item If the game is convex, Shapley value is in core.
        \item Convexity Condition:
        \begin{center}
          $v(A \cup B) \geq v(A) + v(B) - v(A \cap B)$ \\
          $\Leftrightarrow$  \\
          $\forall S,T | S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N,$ \\
          {\color{blue} $v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)$ }
        \end{center}
        \item Depth-1 Convexity Check: $O(n)$
        \item Depth-2 Convexity Check: $O(n^2)$
    \end{itemize}

@@

\begin{frame}{Scenario Two: Web Services and Many Communities}
    \begin{itemize}
        \item Based on Coalition Structure theory
        \begin{itemize}
            \item What coalitions to form?
            \item Stability in coalition structure, is a partition of players, where no other partition can provide all agents with better utility.
            \item Social welfare: $\operatorname*{arg\,max}_{CS} v(CS)$ where $v(CS) = \sum_{C \in CS}v(C)$.
        \end{itemize}
        \item Has to be distributed not centralized
        \item Merge and Split Algorithm {\footnotesize{\color{blue}{(Krzysztof R. Apt and Andreas Witzel)}}}
        \begin{itemize}
            \item Iterative
            \item Converges to a final partition
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.5 \columnwidth]{figures/scenario2.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}       	
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{$\epsilon$-Core}
    \begin{itemize}
        \item The core may not always be non-empty, core is a strong condition
        \item $\epsilon$-core relaxes the core condition
        \item $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon$
        \item relative e-core: $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq (1-\epsilon).v(S)$
    \end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Different Compact Representations of Coalition Games}
